The \dealii Library, Version 9.6

### 2024-07-11 9.6/paper.tex
Describe steps 83 and 86.

Many of the \dealii tutorial programs were revised in a variety of ways
as part of this release. In addition, there are a number of new tutorial
programs:
\begin{itemize}
  \item
    \texttt{step-83} if we can get it ready TODO  
  \item
    \texttt{step-86} if we can get it merged TODO  
  \item
    \texttt{step-87} was contributed by Magdalena Schreter-Fleischhacker
    (Technical University of Munich) and Peter Munch
    (University of Augsburg/Uppsala University). It
    presents the advanced point-evaluation functionalities of \dealii
    that are useful for evaluating finite element solutions at
    arbitrary points on finite element meshes that can be distributed among processes.
  \item
    \texttt{step-89} was contributed by Johannes Heinz (TU Wien),
    Maximilian Bergbauer (Technical University of Munich),
    Marco Feder (SISSA), and Peter Munch (University of Augsburg/Uppsala University).
    It shows one way how to apply non-matching and/or Chimera methods
    within matrix-free loops in \dealii.
  \item
    \texttt{step-90} was contributed by Vladimir Yushutin and Timo Heister (Clemson University).
    It implements the trace finite element method (TraceFEM). TraceFEM solves PDEs
    posed on a, possibly evolving, $(dim-1)$-dimensional surface $\Gamma$ employing
    a fixed uniform background mesh of a $dim$-dimensional domain in which
    the surface is embedded. Such surface PDEs arise in problems involving
    material films with complex properties and in other situations in which
    a non-trivial condition is imposed on either a stationary or a moving interface.
    The program considers a steady, complex, non-trivial surface and the prototypical
    Laplace-Beltrami equation which is a counterpart of
    the Poisson problem on flat domains.
\end{itemize}

>>>>

Many of the \dealii tutorial programs were revised in a variety of ways
as part of this release. In addition, there are a number of new tutorial
programs:
\begin{itemize}
  \item
    \texttt{step-83} \todo{if we can get it merged}
    demonstrates how one can implement
    checkpoint/restart functionality in \dealii{}-based programs,
    using the BOOST serialization functionality as a
    foundation. step-83 was written by Pasquale Africa, Wolfgang
    Bangerth, and Bruno Blais and uses step-19 as its basis.
  \item
    \texttt{step-86} \todo{if we can get it merged}
    is a program that solves the heat equation using PETSc's TS (time
    stepping) framework for the solution of ordinary differential
    equations. Written by Wolfgang Bangerth (Colorado State
    University), Luca Heltai (University of Pisa), and Stefano Zampini
    (King Abdullah University of Science and Technology), it
    illustrates how PDE solvers for time-dependent problems can be
    integrated with existing ODE solver packages to use advanced ODE
    solver concepts (such as higher-order time integration methods and
    adaptive time step control), all without sacrificing the things
    that have traditionally led code authors toward writing their own
    time stepping routines (such as wanting to change the mesh every
    once in a while, or having to deal with boundary conditions).
  \item
    \texttt{step-87} was contributed by Magdalena Schreter-Fleischhacker
    (Technical University of Munich) and Peter Munch
    (University of Augsburg/Uppsala University). It
    presents the advanced point-evaluation functionalities of \dealii
    that are useful for evaluating finite element solutions at
    arbitrary points on finite element meshes that can be distributed among processes.
  \item
    \texttt{step-89} was contributed by Johannes Heinz (TU Wien),
    Maximilian Bergbauer (Technical University of Munich),
    Marco Feder (SISSA), and Peter Munch (University of Augsburg/Uppsala University).
    It shows one way how to apply non-matching and/or Chimera methods
    within matrix-free loops in \dealii.
  \item
    \texttt{step-90} was contributed by Vladimir Yushutin and Timo Heister (Clemson University).
    It implements the trace finite element method (TraceFEM). TraceFEM solves PDEs
    posed on a, possibly evolving, $(dim-1)$-dimensional surface $\Gamma$ employing
    a fixed uniform background mesh of a $dim$-dimensional domain in which
    the surface is embedded. Such surface PDEs arise in problems involving
    material films with complex properties and in other situations in which
    a non-trivial condition is imposed on either a stationary or a moving interface.
    The program considers a steady, complex, non-trivial surface and the prototypical
    Laplace-Beltrami equation which is a counterpart of
    the Poisson problem on flat domains.
\end{itemize}
